---
title: "Week 6 - Who were the winners?"
author: "IMS"
output: html
---

At the conclusion of the ASDN project the PIs decided to hand out first, second, and third prizes to the observers who 
measured the most eggs. Who won? Please use R and dbplyr to answer this question, and please submit your R code. Your code should print out:

```
# Ordered by: desc(total_eggs)
  Name            total_eggs
  <chr>                <int>
1 Vanessa Loverti        163
2 Dylan Kessler           87
3 Richard Lanctot         50
```

You’ll want to load database tables using statements such as:

```
egg_table <- tbl(conn, "Bird_eggs")
```
```{r}
library(duckdb)
library(tidyverse)
```
```{r}
conn <- DBI::dbConnect(duckdb::duckdb(), dbdir="bren-eds213-data/database/database.db")
egg_table <- tbl(conn, "Bird_eggs")
nest_table <- tbl(conn, "Bird_nests")
personnel_table  <- tbl(conn, "Personnel")
```

```{r}
egg_table %>% head()
nest_table %>% head()
personnel_table %>% head()
```

and then use tidyverse grouping, summarization, joining, and other functions to compute the desired result.

```{r}
nest_table %>%
  inner_join(personnel_table, by = c("Observer" = "Abbreviation")) %>%
  inner_join(egg_table, by = c("Nest_ID", "Year", "Site", "Book_page")) %>%
  group_by(Name) %>%
  summarize(
    total_eggs = n()
  ) %>%
  arrange(desc(total_eggs)) %>%
  head(3)
```

Also, take your final expression and pipe it into show_query(). 

```{r}
nest_table %>%
  inner_join(personnel_table, by = c("Observer" = "Abbreviation")) %>%
  inner_join(egg_table, by = c("Nest_ID", "Year", "Site", "Book_page")) %>%
  group_by(Name) %>%
  summarize(
    total_eggs = n()
  ) %>%
  arrange(desc(total_eggs)) %>%
  head(3) %>%
  show_query()
```

If you used multiple R statements, did dbplyr create a temporary table, or did it manage to do everything in one query? Did it limit to the first three rows using an R expression or an SQL LIMIT clause?


*No there is no temporary table. it is one single query.
It limited to the first three rows using an SQL limit clause*